Online appendix for "Who Cares About Crackdowns? Exploring the Role of Trust in Individual Philanthropy

### 2021-04-22 manuscript/appendix.Rmd
Use consistent fonts

---
title: 'Online appendix for "Who Cares About Crackdowns? Exploring the Role of Trust in Individual Philanthropy"'
short-title: 'Online appendix for "Who Cares About Crackdowns?"'
author:
- name: Suparna Chaudhry
  affiliation: Lewis & Clark College
  url: http://www.suparnachaudhry.com/
  email: schaudhry@lclark.edu
- name: Marc Dotson
  affiliation: Brigham Young University
  url: https://marriottschool.byu.edu/directory/details?id=50683
  email: marc_dotson@byu.edu
- name: Andrew Heiss
  affiliation: Georgia State University
  url: https://www.andrewheiss.com/
  email: aheiss@gsu.edu
date: "April 22, 2021"
title-page: false
# published: Working paper.
code-repo: "Access the code and full analysis notebook at <https://stats.andrewheiss.com/who-cares-about-crackdowns/>"
reference-section-title: References
toc: true
appendix: true
editor_options: 
  chunk_output_type: console
---

>>>>

---
title: 'Online appendix for "Who Cares About Crackdowns? Exploring the Role of Trust in Individual Philanthropy"'
short-title: 'Online appendix for "Who Cares About Crackdowns?"'
author:
- name: Suparna Chaudhry
  affiliation: Lewis & Clark College
  url: http://www.suparnachaudhry.com/
  email: schaudhry@lclark.edu
- name: Marc Dotson
  affiliation: Brigham Young University
  url: https://marriottschool.byu.edu/directory/details?id=50683
  email: marc_dotson@byu.edu
- name: Andrew Heiss
  affiliation: Georgia State University
  url: https://www.andrewheiss.com/
  email: aheiss@gsu.edu
date: "April 22, 2021"
title-page: false
# published: Working paper.
code-repo: "Access the code and full analysis notebook at <https://stats.andrewheiss.com/who-cares-about-crackdowns/>"
reference-section-title: References
toc: true
appendix: true
mainfont: Lora
sansfont: IBM Plex Sans
editor_options: 
  chunk_output_type: console
---
